---
title: "Network Analysis"
output:
  html_document: default
  pdf_document: default
---
<style>
body {
text-align: justify}
</style>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

**Network Analysis** examines the relationship among entities, such as persons, organisations, or documents.
It also shows the relationship amongst the entities and how they operate in relation to one another.
If you are using any social media applications, you may have experienced the friend or follower suggestions 
functions. Have you ever wondered how these functions work? One common technology used in these cases is Network Analysis.

It consists of **Nodes** and **edges**. The nodes represent the objects on investigation while the edges represent the relationship 
amongst them.
A crucial application of network analysis is identifying the important node in a network. This task is called Measuring Network '
Centrality. In social network analysis, it can refer to the task of identifying the most influential member, or the representative
 of the group. In r it is done as follows;
 
```{r}
# Importing the Packages --------------------------------------------------

library(pacman)
p_load(visNetwork, igraph, RColorBrewer, dplyr, readxl)
# Data from Kaggle --------------------------------------------------------

setwd("E:/Desktop/Network Analysis")
Inodes <- read.csv("InputFileNodes.csv")
Iedges <- read.csv("InputFileEdges.csv")

Inodes |> 
  View()
Iedges |> 
  View()


# Preparing the nodes -----------------------------------------------------

colors <- colorRampPalette(brewer.pal(3, "OrRd"))(3)
Inodes <- Inodes |> 
  mutate(
  shape = "dot",
  shadow = TRUE,
  title = type.label,
  label = media,
  size = 25,
  borderwidth = 2,
  color.background = colors[media.type],
  color.highlight.background = "yellow",
  color.highlight.border = "black"
  )


# Preparing the edges -----------------------------------------------------

Iedges <- Iedges |> 
  mutate(
    arrows = "to",
    color = "royalblue",
    smooth = TRUE
  )
visNetwork(Inodes, Iedges, main = "The flow of News in different stations") |> 
  visLayout(randomSeed = 5) |> 
  visOptions(highlightNearest = TRUE,
             manipulation = TRUE,
             nodesIdSelection = FALSE) |> 
  visLegend()
```
 
 
 